Greenhouse gas emissions model

### 2021-10-17 211003_scenarios.Rmd
farm scenario update

```{r scenario_sampler}
scenario_sampler<-function(base_estimate, scenarios, model_function, randomMethod = "calculate", functionSyntax="data.frameNames",
  relativeTolerance = 0.05,
  verbosity = 0)
{
  initial_estimate = estimate_read_csv(base_estimate)
  scenarios<-read.csv(scenarios)

@@

  for(scens in scenario_names)
  {
    estim<-initial_estimate
    for (i in 2:nrow(scenarios))
    {if(scenarios$param[i]=="both")
      {estim$marginal[scenarios[i,1],"lower"]<-as.numeric(scenarios[i,scens])
       estim$marginal[scenarios[i,1],"upper"]<-as.numeric(scenarios[i,scens])}
     if(scenarios$param[i]=="lower")
       estim$marginal[scenarios[i,1],"lower"]<-as.numeric(scenarios[i,scens])
     if(scenarios$param[i]=="upper")
       estim$marginal[scenarios[i,1],"upper"]<-as.numeric(scenarios[i,scens])
     if(scenarios$param[i]=="distribution")
       estim$marginal[scenarios[i,1],"distribution"]<-scenarios[i,scens]
     }
    scen_results<-mcSimulation(
      estimate = estim,
      model_function = model_function,
      numberOfModelRuns = as.numeric(scenarios[which(scenarios[1,]=="Runs"),scens]),
      functionSyntax = functionSyntax)
    scen_results$x[,"Scenario"]<-scens
    scen_results$y[,"Scenario"]<-scens
    if(scens==scenario_names[1])
      end_results<-scen_results
    if(!scens==scenario_names[1])
    {end_results$x<-rbind(end_results$x,scen_results$x)
     end_results$y<-rbind(end_results$y,scen_results$y)
     end_results$call<-"multi-scenario call"
     }

>>>>

```{r scenario_sampler}
scenario_sampler<-function(base_estimate, scenarios, model_function, ..., numberOfModelRuns=NA, randomMethod = "calculate", functionSyntax="data.frameNames",
  relativeTolerance = 0.05,
  verbosity = 0)
{
  initial_estimate = estimate_read_csv(base_estimate)
  scenarios<-read.csv(scenarios)

@@

  for(scens in scenario_names)
  {
    estim<-initial_estimate
    for (i in 2:nrow(scenarios))
    {if(scenarios$param[i]=="both")
      {estim$marginal[scenarios[i,1],"lower"]<-as.numeric(scenarios[i,scens])
       estim$marginal[scenarios[i,1],"upper"]<-as.numeric(scenarios[i,scens])}
     if(scenarios$param[i]=="lower")
       estim$marginal[scenarios[i,1],"lower"]<-as.numeric(scenarios[i,scens])
     if(scenarios$param[i]=="upper")
       estim$marginal[scenarios[i,1],"upper"]<-as.numeric(scenarios[i,scens])
     if(scenarios$param[i]=="distribution")
       estim$marginal[scenarios[i,1],"distribution"]<-scenarios[i,scens]
    }

    if("Runs" %in% scenarios[1,])
      n_Runs<-as.numeric(scenarios[which(scenarios[1,]=="Runs"),scens]) else
        if(!is.na(numberOfModelRuns))
          n_Runs<-numberOfModelRuns else
            stop(paste("Not clear how many times scenario", scens, "should be run"))
      if(!(n_Runs==round(n_Runs))&(n_Runs>0))
        stop(paste("Number of runs for scenario", scens, "is not a positive integer"))
    scen_results<-mcSimulation(
      estimate = estim,
      model_function = model_function,
      ...,
      numberOfModelRuns = n_Runs,
      functionSyntax = functionSyntax)
    scen_results$x[,"Scenario"]<-scens
    scen_results$y[,"Scenario"]<-scens
    if(scens==scenario_names[1])
      end_results<-scen_results
    if(!scens==scenario_names[1])
    {end_results$x<-rbind(end_results$x,scen_results$x)
     end_results$y<-rbind(end_results$y,scen_results$y)
     end_results$call<-"multi-scenario call"
     }

### 2021-10-17 211016_GHG_model.Rmd
farm scenario update

---
title: "Greenhouse gas emissions model - making scenarios"
author: "Cory Whitney and Eike Luedeling"
bibliography:
 - references/packages.bib
 - references/papers.bib
output: html_document
---

We're defining the function as in 210617_GHG_model.Rmd, but there's no need to show this again here.

@@

```{r, warning = F, include = F}
#install and load packages
library(DiagrammeR)
library(decisionSupport)
library(ggplot2)
library(plyr)
library(rmarkdown)
# devtools::install_github("CWWhitney/uncertainty")
library(uncertainty)

@@

```{r load_data, include=FALSE}
library(DiagrammeR)
library(decisionSupport)
library(plyr)
library(magrittr)
library(kableExtra)
### # This project will be stored in relative file paths (i.e. same or lower folders)

@@

```{r make_variables, include=FALSE}

@@

```{r ghg_emissions_function, include=FALSE}
# Generate the GHG emissions function 
ghg_emissions<-function(x, varnames){

@@

# question 1: how much of the manure is centrally collected? share_centrally
# question 2: of manure that's not centrally collected, how much is burned? share_central_burn
mms_burn<-(1-share_centrally)*share_central_burn
mms_pasture<-(1-share_centrally)*(1-share_central_burn)

# question 3: of centrally collected manure, how much is spread daily on cropland or pasture? share_spread
mms_spread<-share_centrally*share_spread
not_spread<-share_centrally*(1-share_spread)
# question 4: how much of the manure that's not spread is sold? share_sold
mms_sold<-not_spread*share_sold
not_sold<-not_spread*(1-share_sold)
# question 5: how much of the stored manure that's not sold is stored in liquid form? share_liquid
liquid<-not_sold*share_liquid
solid<-not_sold*(1-share_liquid)
# question 6: how much of the liquid manure is converted to biogas? share_biogas
mms_biogas<-liquid*share_biogas
mms_liquid_slurry<-liquid*(1-share_biogas)
# question 7: how much of the solid manure is composted? share_compost
mms_composted<-solid*share_compost
remain_solid<-solid*(1-share_compost)
# question 8: how much of the solid manure is stored in dry lots? share_drylot
mms_drylot<-remain_solid*share_drylot
mms_solidstore<-remain_solid*(1-share_drylot)

# CH4 emission factor from manure management (Equation 10.23)
mm_ch4<-(volsol*365)*
        (Bo*0.67*
           ((mms_pasture*MCFpasture)+
            (mms_spread*MCFspread)+
            (mms_drylot*MCFdrylot)+
            (mms_solidstore*MCFsolidstore)+
            (mms_composted*MCFcomposted)+
            (mms_liquid_slurry*MCFliquid)+
            (mms_biogas*MCFbiogas)+
            (mms_burn*MCFburn)+
              # CW EL Comment ####
              # the original code was lacking the 'sold' fraction - we added this for completeness
            (mms_sold*MCFsold)))

@@

# estimate N retention (kg/animal/day) (Equation 10.33)
N_retention<-((milk_yield*(1.9+0.4*milk_fat)/100)/6.38)+
  ((weight_gain_WG*(268-(7.03*NE_growth/weight_gain_WG)))/(1000*6.25))

@@

# Direct nitrous oxide emissions (kg N2O/animal/yr) (Eq 10.25 from IPCC guidelines)
mm_direct_n2o<-N_excretion*((mms_pasture*mndec_pasture)+
                           (mms_spread*mndec_spread)+
                           (mms_drylot*mndec_drylot)+
                           (mms_solidstore*mndec_solidstore)+
                           (mms_composted*mndec_composted)+
                           (mms_liquid_slurry*mndec_liquid)+
                           (mms_biogas*mndec_biogas)+
                           (mms_burn*mndec_burn)+
                           (mms_sold*mndec_sold))*(44/28)

# N losses from volatilization (kg N/animal/yr) (Eq 10.26 from IPCC guidelines)
mm_vol_n<-N_excretion*((mms_pasture*mnvc_pasture)+
                           (mms_spread*mnvc_spread)+
                           (mms_drylot*mnvc_drylot)+
                           (mms_solidstore*mnvc_solidstore)+
                           (mms_composted*mnvc_composted)+
                           (mms_liquid_slurry*mnvc_liquid)+
                           (mms_biogas*mnvc_biogas)+
                           (mms_burn*mnvc_burn)+
                           (mms_sold*mnvc_sold))

@@

# Nitrous oxide (N2O) from leaching (kg N/animal/year) (equation 10.28)
mm_leach_n<-N_excretion*((mms_pasture*frac_leach_pasture)+
                           (mms_spread*frac_leach_spread)+
                           (mms_drylot*frac_leach_drylot)+
                           (mms_solidstore*frac_leach_solidstore)+
                           (mms_composted*frac_leach_composted)+
                           (mms_liquid_slurry*frac_leach_liquid)+
                           (mms_biogas*frac_leach_biogas)+
                           (mms_burn*frac_leach_burn)+
                           (mms_sold*frac_leach_sold))

@@

feed_CO2<-feed_prod_CO2*feed_trans_CO2

@@

## Running the model with scenarios

The normal mcSimulation function takes random draws for each of the input variables from the distributions specified in the input table. The distributions that are used are the same for every run of the Monte Carlo simulation. Sometimes it's desirable to specify particular scenarios *a priori*, e.g. to simulate outcomes for particular farm types, climate scenarios etc. To do this, we would normally have to define separate input tables and run separate simulations. This is quite inconvenient. Here, we'll develop a function that can do this job automatically.

The new function will consist of a wrapper around the mcSimulation function, which will be able to modify the input table according to a scenario file we provide. This file will contain information on which variables should be modified for each scenario and how many model runs should be included in the simulation.

```{r scenario_sampler}
scenario_sampler<-function(base_estimate, scenarios, model_function, ..., numberOfModelRuns=NA, randomMethod = "calculate", functionSyntax="data.frameNames",
  relativeTolerance = 0.05,
  verbosity = 0)
{
  initial_estimate = estimate_read_csv(base_estimate)
  scenarios<-read.csv(scenarios)

  scenario_names<-colnames(scenarios[3:ncol(scenarios)])

  for(scens in scenario_names)
  {
    estim<-initial_estimate
    for (i in 2:nrow(scenarios))
    {if(scenarios$param[i]=="both")
      {estim$marginal[scenarios[i,1],"lower"]<-as.numeric(scenarios[i,scens])
       estim$marginal[scenarios[i,1],"upper"]<-as.numeric(scenarios[i,scens])}
     if(scenarios$param[i]=="lower")
       estim$marginal[scenarios[i,1],"lower"]<-as.numeric(scenarios[i,scens])
     if(scenarios$param[i]=="upper")
       estim$marginal[scenarios[i,1],"upper"]<-as.numeric(scenarios[i,scens])
     if(scenarios$param[i]=="distribution")
       estim$marginal[scenarios[i,1],"distribution"]<-scenarios[i,scens]
    }

    if("Runs" %in% scenarios[1,])
      n_Runs<-as.numeric(scenarios[which(scenarios[1,]=="Runs"),scens]) else
        if(!is.na(numberOfModelRuns))
          n_Runs<-numberOfModelRuns else
            stop(paste("Not clear how many times scenario", scens, "should be run"))
      if(!(n_Runs==round(n_Runs))&(n_Runs>0))
        stop(paste("Number of runs for scenario", scens, "is not a positive integer"))
    scen_results<-mcSimulation(
      estimate = estim,
      model_function = model_function,
      ...,
      numberOfModelRuns = n_Runs,
      functionSyntax = functionSyntax)
    scen_results$x[,"Scenario"]<-scens
    scen_results$y[,"Scenario"]<-scens
    if(scens==scenario_names[1])
      end_results<-scen_results
    if(!scens==scenario_names[1])
    {end_results$x<-rbind(end_results$x,scen_results$x)
     end_results$y<-rbind(end_results$y,scen_results$y)
     end_results$call<-"multi-scenario call"
     }

  }
  class(end_results) <- cbind("mcSimulation", class(end_results))
  return(end_results)
}

@@

This function does the same as the mcSimulation function, but with an additional scenario_file that can be supplied. This file specifies which variables should be modified for each of the scenarios, as well as the number of model runs for for it. Here's an example file:

```{r}
knitr::kable(read.csv("data/scenarios.csv"))

@@

Each column beyond the first two columns contains information for a particular scenario. This is restricted to the parameters that should be *changed* for this scenario. All variables that aren't specified in this table remain at their original values given in the usual input table (which is called `base_estimate` here).

The first row ("Runs" in the first column) indicates the number of runs.

Each subsequent row indicates which value from the input table should be modified, so the string in the first column has to correspond to a variable name in the input table. The second column indicates which value should be changes, with options being "lower", "upper", "distribution" and "both". If "both" is selected, both the lower and upper bounds are modified (this should only be done for constants).

```{r monte_carlo_simulation}

GHG_simulation<-scenario_sampler(base_estimate = "data/livestock_ghg_input_table.csv",
                                 scenarios = "data/scenarios.csv",
                                 model_function = ghg_emissions,
                                 functionSyntax = "plainNames")

#GHG_simulation <- mcSimulation(
#  estimate = estimate_read_csv("data/livestock_ghg_input_table.csv"),
#  model_function = ghg_emissions,
#  numberOfModelRuns = 1e4, # 10,000 runs
#  functionSyntax = "plainNames"
#)
```

@@

@@

@@

@@

@@

@@

@@

@@

# plot with patchwork
layout <- "
           AAABBB
           CCCDDD
           EEEFFF
           GGGGGG
          "

enteric_CH4_dist_plot + milk_yield_dist_plot + 
  enteric_CH4_CO2eq_dist_plot + mm_CH4_CO2eq_dist_plot + 
  mm_N2O_CO2eq_dist_plot + feed_CO2_dist_plot + 
  on_farm_dist_plot + 
plot_layout(guides = "collect", design = layout) 
```

@@

```{r}
GHG_simulation_PLS<-GHG_simulation
GHG_simulation_PLS$x<-GHG_simulation_PLS$x[,1:ncol(GHG_simulation_PLS$x)-1]
GHG_simulation_PLS$y<-GHG_simulation_PLS$y[,1:ncol(GHG_simulation_PLS$y)-1]

pls_result <- plsr.mcSimulation(object = GHG_simulation_PLS,
                  resultName = names(GHG_simulation_PLS$y)[7], ncomp = 1)
```

We run the `plot_pls()` on the results from `plsr.mcSimulation()` with a number of standard settings. The length of the bars is equal to VIP with a vertical line at '1' on the x-axis indicating a standard cut-off for VIP used for variable selection [@Whitney2017]. The overall plot only shows those variables with a VIP > 0.8, which is the common threshold for variable selection [@Lanzanova2019, @Luedeling2016]. The colors of the bars represent the positive or negative coefficient of the given input variable with the output variable.

@@

We apply the uncertainty functions on the `milk_yield` and `on_farm` variables. These come from the model results (`r nrow(GHG_simulation$y)`) of the `GHG_simulation` model results to the `in_var` (x) and an outcome variable `out_var` (y). in the model we defined `on_farm` as the sum of Carbon Dioxide Equivalent Enteric Methane Emissions from Livestock (`enteric_CH4_CO2eq`), Carbon Dioxide Equivalent Methane Emissions from Livestock Manure (`mm_CH4_CO2eq`), Carbon Dioxide Equivalent Nitrous Oxide Emissions from Livestock Manure (`mm_N2O_CO2eq`) and Carbon Dioxide Emissions from Livestock Feed Production and Transport (`feed_CO2`).

```{r name_in_out_vars}
in_var  <- GHG_simulation$y$milk_yield
out_var <- GHG_simulation$y$on_farm
```

>>>>

---
title: "Greenhouse gas emissions model"
author: "Cory Whitney and Eike Luedeling"
bibliography:
 - references/packages.bib
 - references/papers.bib
output: html_document
---

@@

```{r, warning = F, include = F}
#install and load packages
library(DiagrammeR)
library(decisionSupport)
library(ggplot2)
library(plyr)
library(rmarkdown)
#devtools::install_github("CWWhitney/uncertainty")
library(uncertainty)

@@

```{r load_data}
library(DiagrammeR)
library(decisionSupport)
library(plyr)
library(magrittr)
library(kableExtra)
### # This project will be stored in relative file paths (i.e. same or lower folders)

@@

The manure management is based on a decision tree.

## Decision tree for manure management

It is difficult to know with precision how much manure is managed according to each of the management categories. Capturing the corresponding uncertainty is difficult, because estimating each fraction separately is unlikely to add up to 100%. We address this problem with a decision tree.

Each step in the decision tree (each node) represents a share of manure that is managed according to the name of the node. Green arrows indicate 'Yes' and red arrows 'No'. The descriptions for the uses can be found in the IPCC report on manure management chapter 10 [@dong_ipcc_2006].

```{r graph-mermaid-manure, echo=FALSE, fig.width=10, fig.height=1}
mermaid("
        graph LR
        C(Central collection)-->B(Burned); linkStyle 0 stroke: red, stroke-width:1px
                                B-->P(Pasture); linkStyle 1 stroke: red, stroke-width:1px
        C-->D(Daily spread); linkStyle 2 stroke: green, stroke-width:1px
            D-->S(Sold); linkStyle 3 stroke: red, stroke-width:1px
                S-->L(Liquid storage); linkStyle 4 stroke: red, stroke-width:1px
                    L-->Co(Composted); linkStyle 5 stroke: red, stroke-width:1px
                        Co-->Dl(Dry lot); linkStyle 6 stroke: red, stroke-width:1px
                             Dl-->St(Solid storage); linkStyle 7 stroke: red, stroke-width:1px
                    L-->Bi(Biogas); linkStyle 8 stroke: green, stroke-width:1px
                        Bi-->Ls(Liquid); linkStyle 9 stroke: red, stroke-width:1px
        ")
```

## Making variables for model development

Here we generate a `make_variables` function for testing the model function 'line by line'. We use it to take a single random sample of the provided estimates (this isn't required for running the model later, but it helps when developing the code).

```{r make_variables, warning=FALSE}

@@

## The model

The following is our draft of the emissions model, with explanations of all steps (we can format this better once we agree on the final model).

```{r ghg_emissions_function}
# Generate the GHG emissions function 
ghg_emissions<-function(x){

@@

# question 1: how much of the manure is centrally collected? share_centrally
# question 2: of manure that's not centrally collected, how much is burned? share_central_burn
#mms_burn<-(1-share_centrally)*share_central_burn
#mms_pasture<-(1-share_centrally)*(1-share_central_burn)

# question 3: of centrally collected manure, how much is spread daily on cropland or pasture? share_spread
#mms_spread<-share_centrally*share_spread
#not_spread<-share_centrally*(1-share_spread)
# question 4: how much of the manure that's not spread is sold? share_sold
#mms_sold<-not_spread*share_sold
#not_sold<-not_spread*(1-share_sold)
# question 5: how much of the stored manure that's not sold is stored in liquid form? share_liquid
#liquid<-not_sold*share_liquid
#solid<-not_sold*(1-share_liquid)
# question 6: how much of the liquid manure is converted to biogas? share_biogas
#mms_biogas<-liquid*share_biogas
#mms_liquid<-liquid*(1-share_biogas)
# question 7: how much of the solid manure is composted? share_compost
#mms_composted<-solid*share_compost
#remain_solid<-solid*(1-share_compost)
# question 8: how much of the solid manure is stored in dry lots? share_drylot
#mms_drylot<-remain_solid*share_drylot
#mms_solidstore<-remain_solid*(1-share_drylot)

# CH4 emission factor from manure management (Equation 10.23)
mm_ch4<-(volsol*365)*
        (Bo*0.67*
           ((mms_pasture*MCFpasture)+
            (mms_spread*MCFspread)+
            (mms_drylot*MCFdrylot)+
            (mms_solidstore*MCFsolidstore)+
            (mms_composted*MCFcomposted)+
            (mms_liquid*MCFliquid)+
            (mms_biogas*MCFbiogas)+
            (mms_burn*MCFburn)+
              # CW EL Comment ####
              # the original code was lacking the 'sold' fraction - we added this for completeness
            (mms_sold*MCFsold)))

@@

# estimate N retention (kg/animal/day) (Equation 10.33)
if(weight_gain_WG==0)
  N_retention<-((milk_yield*(1.9+0.4*milk_fat)/100)/6.38) else
    N_retention<-((milk_yield*(1.9+0.4*milk_fat)/100)/6.38)+
      ((weight_gain_WG*(268-(7.03*NE_growth/weight_gain_WG)))/(1000*6.25))

@@

# Direct nitrous oxide emissions (kg N2O/animal/yr) (Eq 10.25 from IPCC guidelines)
mm_direct_n2o<-N_excretion*((mms_pasture*mndec_pasture)+
                           (mms_spread*mndec_spread)+
                           (mms_drylot*mndec_drylot)+
                           (mms_solidstore*mndec_solidstore)+
                           (mms_composted*mndec_composted)+
                           (mms_liquid*mndec_liquid)+
                           (mms_biogas*mndec_biogas)+
                           (mms_burn*mndec_burn)+
                           (mms_sold*mndec_sold))*(44/28)

# N losses from volatilization (kg N/animal/yr) (Eq 10.26 from IPCC guidelines)
mm_vol_n<-N_excretion*((mms_pasture*mnvc_pasture)+
                           (mms_spread*mnvc_spread)+
                           (mms_drylot*mnvc_drylot)+
                           (mms_solidstore*mnvc_solidstore)+
                           (mms_composted*mnvc_composted)+
                           (mms_liquid*mnvc_liquid)+
                           (mms_biogas*mnvc_biogas)+
                           (mms_burn*mnvc_burn)+
                           (mms_sold*mnvc_sold))

@@

# Nitrous oxide (N2O) from leaching (kg N/animal/year) (equation 10.28)
mm_leach_n<-N_excretion*((mms_pasture*frac_leach_pasture)+
                           (mms_spread*frac_leach_spread)+
                           (mms_drylot*frac_leach_drylot)+
                           (mms_solidstore*frac_leach_solidstore)+
                           (mms_composted*frac_leach_composted)+
                           (mms_liquid*frac_leach_liquid)+
                           (mms_biogas*frac_leach_biogas)+
                           (mms_burn*frac_leach_burn)+
                           (mms_sold*frac_leach_sold))

@@

feed_CO2<-feed_prod_CO2+feed_trans_CO2

@@

## Running the model

We apply the `decisionSupport` tools for running the Monte Carlo simulation [@R-decisionSupport]. See the vignette guides on *applying the mcSimulation function* [@fernandez_applying_2021] and *simulating the cost effectiveness of controlled burning* [@whitney_simulating_2017] for examples.

```{r monte_carlo_simulation, warning=FALSE}
GHG_simulation <- mcSimulation(
  estimate = estimate_read_csv("data/livestock_ghg_input_table.csv"),
  model_function = ghg_emissions,
  numberOfModelRuns = 1e4, # 10,000 runs
  functionSyntax = "plainNames"
)
```

As of version 1.107 of `decisionSupport`, the package contains the `scenario_mc` function, which allows specifying different distributions of the input variables for specific subsets of the total number of model runs. We'll use this functionality here to simulate results for actual herd compositions encountered in Kenya.

```{r scenario_making}
Kenya_herds<-read.csv("data/Kenya_baseline_individual_cow_wNotes.csv")

herds<-table(Kenya_herds[,c("QQNO","animal_type")])

mms<-t(aggregate(Kenya_herds[,c("mms_pasture","mms_spread","mms_drylot","mms_solidstore","mms_composted","mms_liquid","mms_biogas","mms_burn","system","feed_kgCO2","feed_transport_kgCO2")],by=list(Kenya_herds$QQNO), FUN=median))
mms<-mms[2:nrow(mms),]
rownames(mms)[which(rownames(mms)=="system")]<-"feeding_system"
rownames(mms)[which(rownames(mms)=="feed_kgCO2")]<-"feed_prod_CO2"
rownames(mms)[which(rownames(mms)=="feed_transport_kgCO2")]<-"feed_trans_CO2"

herd_scenarios<-cbind(data.frame(Variable=paste0("N_animal_type_",1:12),param=rep("both",12)),
                      as.data.frame.matrix(t(herds)))
colnames(herd_scenarios)[3:ncol(herd_scenarios)]<-paste0("farm_",1:(ncol(herd_scenarios)-2))

mms_scenarios<-cbind(data.frame(Variable=rownames(mms),param=rep("both",nrow(mms))),
                     as.data.frame.matrix(mms))
colnames(mms_scenarios)[3:ncol(mms_scenarios)]<-paste0("farm_",1:(ncol(mms_scenarios)-2))

scenarios<-rbind(herd_scenarios,mms_scenarios)

scenarios[,1:7]   %>%
    kableExtra::kbl(digits = 2)  %>%
    kableExtra::kable_classic_2(full_width = F)

@@

With these scenarios, we can now feed the Monte Carlo simulation with realistic farm compositions. To adequately consider uncertainty, we can run a user-specified number of random scenarios for each farm.

```{r scenario_runs, warning=FALSE}

GHG_simulation_real_farms<-scenario_mc(base_estimate=estimate_read_csv("data/livestock_ghg_input_table.csv"),
                     scenarios=scenarios,
                     model_function = ghg_emissions,
                     numberOfModelRuns = 10,
                       functionSyntax="plainNames")

@@

@@

enteric_CH4_dist_plot_farms <- plot_distributions(mcSimulation_object = GHG_simulation_real_farms,
                   vars = "enteric_CH4",
                   method = "boxplot_density",
                   old_names = "enteric_CH4",
                   new_names = "Total Methane Emissions from Livestock by Enteric Fermentation") + 
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())

@@

milk_yield_dist_plot_farms <- plot_distributions(mcSimulation_object = GHG_simulation_real_farms,
                   vars = "milk_yield",
                   method = "boxplot_density",
                   old_names = "milk_yield",
                   new_names = "Total Milk Yield") + 
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())

@@

enteric_CH4_CO2eq_dist_plot_farms <- plot_distributions(mcSimulation_object = GHG_simulation_real_farms,
                   vars = "enteric_CH4_CO2eq",
                   method = "boxplot_density",
                   old_names = "enteric_CH4_CO2eq",
                   new_names = "Carbon Dioxide Equivalent Enteric Methane Emissions from Livestock") + 
  theme(axis.title.x=element_blank())

@@

mm_CH4_CO2eq_dist_plot_farms <- plot_distributions(mcSimulation_object = GHG_simulation_real_farms,
                   vars = "mm_CH4_CO2eq",
                   method = "boxplot_density",
                   old_names = "mm_CH4_CO2eq",
                   new_names = "Carbon Dioxide Equivalent Methane Emissions from Livestock Manure") + 
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())

@@

mm_N2O_CO2eq_dist_plot_farms <- plot_distributions(mcSimulation_object = GHG_simulation_real_farms,
                   vars = "mm_N2O_CO2eq",
                   method = "boxplot_density",
                   old_names = "mm_N2O_CO2eq",
                   new_names = "Carbon Dioxide Equivalent Nitrous Oxide Emissions from Livestock Manure") + 
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())

@@

feed_CO2_dist_plot_farms <- plot_distributions(mcSimulation_object = GHG_simulation_real_farms,
                   vars = "feed_CO2",
                   method = "boxplot_density",
                   old_names = "feed_CO2",
                   new_names = "Carbon Dioxide Emissions from Livestock Feed Production and Transport") + 
  theme(axis.title.x=element_blank(),
        axis.title.y=element_blank())

@@

on_farm_dist_plot_farms <- plot_distributions(mcSimulation_object = GHG_simulation_real_farms,
                   vars = "on_farm",
                   method = "boxplot_density",
                   old_names = "on_farm",
                   new_names = "Total Carbon Dioxide Equivalent Emissions from Livestock") + 
  theme(axis.title.y=element_blank())

@@

# plot with patchwork
layout <- "
           AAABBB
           CCCDDD
           EEEFFF
           GGGGGG
          "
```

Here's the plot that results from using the same parameters for all farms:

```{r}
enteric_CH4_dist_plot + milk_yield_dist_plot + 
  enteric_CH4_CO2eq_dist_plot + mm_CH4_CO2eq_dist_plot + 
  mm_N2O_CO2eq_dist_plot + feed_CO2_dist_plot + 
  on_farm_dist_plot + 
plot_layout(guides = "collect", design = layout)

And here's what happens when we run 10 random scenarios for each real herd composition:

```{r}
enteric_CH4_dist_plot_farms + milk_yield_dist_plot_farms + 
  enteric_CH4_CO2eq_dist_plot_farms + mm_CH4_CO2eq_dist_plot_farms + 
  mm_N2O_CO2eq_dist_plot_farms + feed_CO2_dist_plot_farms + 
  on_farm_dist_plot_farms + 
plot_layout(guides = "collect", design = layout)

@@

```{r}
pls_input<-GHG_simulation_real_farms
pls_input$x<-pls_input$x[,which(!("Scenario" == colnames(pls_input$x)))]
pls_result <- plsr.mcSimulation(object = pls_input,
                  resultName = names(pls_input$y)[7], ncomp = 1)
```

We run the `plot_pls()` on the results from `plsr.mcSimulation()` with a number of standard settings. The length of the bars is equal to VIP with a vertical line at '1' on the x-axis indicating a standard cut-off for VIP used for variable selection [@whitney_simulating_2017]. The overall plot only shows those variables with a VIP > 0.8, which is the common threshold for variable selection [@lanzanovaImprovingDevelopmentEfficiency2019b, @luedeling2016decision]. The colors of the bars represent the positive or negative coefficient of the given input variable with the output variable.

@@

We apply the uncertainty functions on the `milk_yield` and `on_farm` variables. These come from the model results (`r nrow(GHG_simulation_real_farms$y)`) of the `GHG_simulation_real_farms` model results to the `in_var` (x) and an outcome variable `out_var` (y). in the model we defined `on_farm` as the sum of Carbon Dioxide Equivalent Enteric Methane Emissions from Livestock (`enteric_CH4_CO2eq`), Carbon Dioxide Equivalent Methane Emissions from Livestock Manure (`mm_CH4_CO2eq`), Carbon Dioxide Equivalent Nitrous Oxide Emissions from Livestock Manure (`mm_N2O_CO2eq`) and Carbon Dioxide Emissions from Livestock Feed Production and Transport (`feed_CO2`).

```{r name_in_out_vars}
in_var  <- GHG_simulation_real_farms$y$milk_yield
out_var <- GHG_simulation_real_farms$y$on_farm
```
